\documentclass[../main.tex]{subfiles}

\begin{document}

\subsection{Background}


\subsection{Related work}

% Part 1

% Part 2
% {{{

% Background 
% {{{{
The second important concept of the project is the computer simulation.
Simulation is a cost-effective, time-saving, flexible 
and safe way to experiment with a drone
at the expense of a reduction in accuracy compared to the real world.
The research realm has shown that the use of simulation 
is highly attractive in \gls{drl} studies with drones.
This is because \gls{drl} involves
making gradual improvements to a model based on 
repeated cycles of experience, and computer simulation 
allows these iterations to be carried out cheaply.

According to the literature review, 
the combination of Gazebo, \gls{ros}
and \textsc{px4} are the most widely used software stack 
for the \gls{sitl} development
because they are open-source. 
In contrast, Sphinx and Olympe, which are used in this project, 
are closed-source.
Although open-source software 
allows for full control and the flexibility to tinker
since the source code is freely available,
it is less stable and time-consuming to debug
when there is an error in the source code.
Another conclusion from the literature is that 
the transfer from simulation to the real world,
which this project also aims to accomplish,
is lacking in the studies reviewed.
As a result, it is not possible to comment on 
how the simulation findings effectively translate
to the physical environment.
% }}}}

% Related work
% {{{{ Zhou2020
% Topic sentence
The use of simulation makes rapid experiments in realistic settings 
and iterative \gls{uav} designs possible, 
both of which are important in \gls{ai} training. 
% Explanation
\citeauthor{Zho20} demonstrates this by % or \textcite{Zho20}
using a combination of the open-source 3D dynamic simulator Gazebo
and the autopilot system \textsc{px4}.
Through this, they avoided the time-consuming steps of 
carrying out physical experiments
and adjusting parameters according 
to the environmental settings~\cite{Zho20}.
Thanks to the simulation, 
the authors were also able to propose a generic
framework to integrate the \gls{dqn} algorithm into 
the simulated \gls{uav} environment~\cite{Zho20}.
In our work, the same Gazebo physics engine
simulation software is used, and \gls{drl} is similarly trained
for the high-level control of the \gls{uav}. 
However, the authors used the \gls{ros}-\textsc{px4} as the controller 
while in our work, the Olympe program is used.
The main criticism against this paper is that the operating system,
which was Ubuntu 16.04, and 
the \gls{ros} version, which was Kinetic Kame, 
were old and no longer supported 
even though the paper was written in 2020.
Nevertheless, the explanation and the flowchart illustrating the 
Q-learning in the context of drone control are instructive 
for our work going forward.
% }}}}

% {{{{ Walker2019
% Topic sentence
The time-saving benefit and the ease of experimentation 
afforded by the use of computer simulation are further emphasized 
when studying uncertain environments.
% Explanation
Dealing with an unknown environment for search and navigation applications,
\citeauthor{Wal19} used simulation to train a \gls{uav}
to solve a local planning problem
by framing the problem as 
a \gls{pomdp}
using continuous action spaces~\cite{Wal19}.
Similar to the previous paper, the \gls{ros}-\textsc{px4} stack 
and the Gazebo 
simulation software were used compared to Olympe and Sphinx 
in this project~\cite{Wal19}.
In addition, both the paper and this project study path planning 
with \gls{drl} but our work uses it for target visitation 
in an obstacle-free environment 
while the authors used it for searching and navigation
in both obstacle-free and non-obstacle-free environments.
However, the use of a \gls{uav} indoor by the authors as an application 
does not leverage the unique features of \glspl{uav}, 
but it is a good starting point 
and easier to implement in the real world 
when the outdoor flight is restricted.
A useful lesson that this paper provides for our project
is the use of the open \gls{ai} gym in creating the \gls{uav} environment
resulting in clearer abstraction in the codebase
for the training process.
% }}}}

% {{{{ Garcia2020
% Topic sentence
Yet another \gls{uav} research-related applications 
that profits from the use of computer simulation 
is the testing of new sensors on the \gls{uav}.
% Evidence 1
\citeauthor{Gar20} argues that the future of \glspl{uav}
relies on the use of advanced sensors and 
the ease of analyzing their functions
in real operational conditions~\cite{Gar20}.
% Response
To demonstrate such viability, they connected a \gls{lidar} sensor
to a PixHawk flight controller and tested the improvement
that the new sensor provided
in the application of navigation and obstacle avoidance.
Importantly, prior to that, they used QGroundControl and the \textsc{px4}
platforms to analyze the addition of a \gls{lidar} sensor
on a simulated 3DR Iris \gls{uav}.
Unlike our work, the authors' focus for using the simulation
was on sensor integration and not \gls{drl} 
which did not feature in the paper. 
The main criticism of this work is that 
the sensor is simulated without noise
when in the real world, the data captured
by the sensor is invariably noisy.
Although the objectives between the authors' and our work
are different, it is still very helpful to learn from
the extensive software stack and architecture guide 
presented by the authors.
% }}}}

% }}}

% Part 3
% {{{
% Background 
% {{{{
		The third and final concept of the project is hardware realization for drone visits.
		The hardware part is essential in the implementation in the real world, where the simulation sometimes strays from the truth.
		There is a lack of hardware implementations in the field of research regarding drones with \gls{drl}, and most of the research papers focus on the simulations.
		According to the literature review, the \gls{cnn} models were used in the majority of the papers for object detection. 
		Also, the controller boards and custom drone kits were used instead of commercial drones.
		Those kits give the researcher and user more flexibility since the drone is customizable 
		in hardware and software.But in our design, we will use a commercial drone so that we focus
		 on the \gls{drl}, not the actual drone build process. 

% }}}}

% Related work
% {{{{ Khan2021
% Topic sentence
	The use of a microcomputer with Quadcopter \glspl{uav} and autopilot software will help in the hardware implementation part.
	% Explanation
	\citeauthor{Khan21} used the drone in the agriculture field to spray 
	pesticides and monitor the crops. Unlike our work, the drone was limited to specific
	boundaries and fixed targets such as crops.
	They used a Raspberry Pi microcomputer board attached to the drone, which will handle two different operations. Firstly, it will control the drone using an open-source
	 software called Arducopter autopilot which will handle the trip of the drone and autonomous 
	 flight option. The second operation is to deal with the Intel neural computer stick 2, which will deploy the \gls{cnn} model and deal with the computation part~\cite{Khan21}.
	Although this work is close to ours, there are some differences, 
	one of them is using a custom drone which is not considered since we are limited in time.
	Since we will use the Anafi drone, the Olympe program will take control of the drone, which will
	 be installed on the Raspberry Pi. Finally, using \gls{cnn} only is not enough without \gls{drl} 
	 which makes the drone more intelligent and accurate.


% }}}}

% {{{{ Wang2018
% Topic sentence
	Commercial drone with onboard computer uses SDK with image processing techniques.
	% Explanation
	The hardware architecture in \citeauthor{Wang18} work for this paper includes a DJI 
	commercial drone and an onboard computer called manifold, which is from the same manufacturer.
	 Also, onboard sensors like camera,\gls{gps} and inertial sensor are included. Finally,
	 external battery for the manifold computer and Wi-Fi adapter that is used for connection 
	 between the drone and the onboard computer. This hardware architecture is inspirational, and our design is somehow close to it with minor changes in the onboard computer and 
	 without the existence of the sensors.Image and video processing techniques were used, such as 
	 segmentation to keep detecting moving targets was presented in ~\cite{Wang18}.
	For the navigation part, they used predetermined waypoints related to historical path cost. 
	However, in our work, probability and mobility patterns will be used to guess the target's location.
% }}}}

% {{{{ Zhao2018
% Topic sentence
    The use of embedded system attached to the \gls{uav} which implements mobility pattern recognition, to decrease response time and save transmission bandwidth. 
	% Explanation 
	\citeauthor{Zhao18} work used a quadrotor \gls{uav} supported with \gls{gps} module and a Pix 
	Hawk flight controller. The power sources in the architecture were two lithium batteries, 
	one for the drone and one for the embedded system. The system uses NVIDIA Jetson development
	 kits which give enough computing power for the processing and communication between the flight 
	 controller and the system. The Jetson board is connected to the flight controller using serial 
	 communication while connected to the ground controller using Wi-Fi. Communication tools and protocols used in \citeauthor{Zhao18} work will help us to determine the best way to communicate between the development board and the drone without any delay or interference ~\cite{Zhao18}. 


% }}}}

% }}}



\end{document}

