\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}

\begin{document}

\newcounter{impactcounter}
\setcounter{impactcounter}{1}
\newcommand\showimpactcounter{%
    \theimpactcounter\stepcounter{impactcounter}%
}

Our project has many impacts and implications on different contexts, mainly 
the global, public, economical, environmental and social context. Further 
explanations about these are mentioned in~\cref{tab:impact}.

\begin{center}
    \begin{xltabular}{\textwidth}{ c L{2.5cm} X X }
        \caption{Impact of the engineered solution on 
        different contexts.}
        \label{tab:impact} \\

	\toprule
	\textit{No} 
	& \textit{Constraint} 
	& \textit{Relevance to the design} 
	& \textit{Justification of the design’s impact} \\
	
	\midrule
        \endfirsthead

        \caption[]{Impact of the engineered solution on 
        different contexts (continued)} \\

	\toprule
	\textit{No} 
	& \textit{Constraint} 
	& \textit{Relevance to the design} 
	& \textit{Justification of the design’s impact} \\
	
	\midrule
        \endhead
	
	\showimpactcounter
	& Public Health, Safety, and Welfare
        & Our solution can help track criminals' locations and
        identify illegal immigration across the border thus enhancing
        home security. 
        & We can use the \gls{ml} part of our framework to detect
        human movements and even identify the suspect based on his
        facial composite. 
        The \gls{rl} will then be trained based on the common
        movements of criminals or illegal immigrants and thus will
        tell the drone where to fly the most effectively.
        Through monitoring the camera feed, the person in-charge can
        take the necessary actions.
        \\ \addlinespace
	
	\showimpactcounter
	& Global Implications
        & Much of the current research for target visitation, as well
        as its applications, can be revolutionized based on our
        project.
	& The techniques used in the different fields could be
        replaced by \gls{rl} the way shown in this project due to its
        proven high efficiency compared to a scanning technique such
        as the zig-zag. 
        \\ \addlinespace
	
	\showimpactcounter
	& Cultural Implications 
        & The solution provided may be used to raise awareness in
        fields such as traffic safety through detecting and penalizing
        bad drivers' behaviors by monitoring and tracking mobile
        vehicles on the highway.
        & Using AI technologies may help detect, track and discover
        reckless drivers' behavior through smart navigation. 
        Also, visual simulation may potentially reduce cost and time
        required for such monitoring.
        \\ \addlinespace
	
	\showimpactcounter
	& Social Implications
	& A part of this project can help regulate behavior in public
        places or high-risk areas, for example, around a football
        stadium during or after a match.
        A person's actions can change positively when they know they are
        being watched, which can be done using our drone.
        & Object detection is a sub-part of our project, and such
        object detection model can be trained to detect inappropriate
        types of behavior.
        The \gls{rl} model can be trained to fly to strategic
        locations that will capture each and every portion of the area
        of interest with a minimal delay between two subsequent
        visitations of the same area.
        \\ \addlinespace
	
	\showimpactcounter
	& Environmental Factors
        & The solution of this project can aid in tracking and
        studying the migration habits of animals which could save them
        and maintain the ecological equilibrium.
        & The object detection model could be retrained to detect some
        type of endangered animals. 
        Also, their movement can be studied and learned by an \gls{rl}
        model.
        \\ \addlinespace
	
	\showimpactcounter
	& Economic Factors  
        & Increased security can have a huge economic benefit by
        avoiding the high cost of a security breach. 
        Moreover, the autonomous drones field might end some jobs but
        it will surely create numerous new ones.
	& Our framework for an autonomous \glspl{uav} for target
        visitation can enable companies to extend their capabilities
        and thus increase their workforce.
        This will directly lead to more job openings.
        \\ \addlinespace
	
	\bottomrule		
    \end{xltabular}
\end{center}

\end{document}
