\documentclass[../main.tex]{subfiles}

\begin{document}
\subsection{Business products}
	Technology and AI advancements have been changing human lives for the better. The possible opportunities for innovation and creativity are unlimited.
	This project has many aspects that could lead to business opportunities and commercial prototypes. 
	One of the many commercial products that could come out of this project is the \gls{drl} object detection model. This model can be used in any system that requires object detection, it could be a \gls{uav}, a CCTV camera, or any system that inputs an image to the model after being trained on a similar data set.
	Depending on the system, the \gls{drl} model could be trained using a different data set to detect a different object (e.g. cars, humans, animals).
	Another possible product is the \gls{drl} model responsible for navigating the drone after being trained on a specific movement pattern.
	Moreover, The entire system developed in this project is a viable product.

\subsection{Interested parties}
	1- Military applications: Drones and object detection models have been used in military operations to detect people of danger or even shoot them.\\
	2- Object tracking could be very helpful for any biological research, i.e. tracking animals' movement and habits in different times could revolutionize biology. \\ 
	3- Security companies: Personal home security could be established by such object detection models to detect threats or unusual behaviors.


\end{document}
