\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}

\begin{document}

\subsection{Project milestones}

\newcounter{milestonecounter}
\newcounter{subcounter}[milestonecounter]
\newcommand\showmilestonecounter{%
    \stepcounter{milestonecounter}%
    \themilestonecounter%
}
\renewcommand{\thesubcounter}{%
    \stepcounter{subcounter}%
    \themilestonecounter.\arabic{subcounter}%
}

% uncomment below before submission
% \input{../tables/milestone-senior-1.tex} 

\input{../tables/milestone.tex}

\subsection{Project timeline}

% uncomment below before submission
% \input{../tables/timeline-senior-1.tex}

\input{../tables/timeline.tex}

\subsection{Anticipated risks}

\begin{center}
    \begin{xltabular}{\textwidth}{ X X X }
        \caption{Anticipated risks.}
        \label{tab:risks} \\
        \toprule
        \textit{Anticipated Risk} 
        & \textit{Description} 
        & \textit{Minimizing approach} \\
        \midrule
        \endfirsthead

        \caption[]{Anticipated risks (continued)} \\
        \toprule
        \textit{Anticipated Risk} 
        & \textit{Description} 
        & \textit{Minimizing approach} \\
        \midrule
        \endhead

        Late delivery of the components 
        & Some components are available online 
        and it takes time to arrive, 
        any delay will affect the hardware implementation.
        & Order early and from trusted sources with previous 
        customers reviews. \\
        
        Loss of connection with the Raspberry Pi
        & Because we are connecting using Wi-Fi, 
        maybe a connection loss 
        happen to due coverage or hardware issue.
        & Code a script to return the drone 
        to the takeoff location 
        and do multiple tests to make sure 
        we cover all the possible cases. \\
        
        Loss of control of the drone
        & Because we are limited in fly time 
        and battery capacity, 
        the drone can shut down immediately if 
        no power reaches it.
        Another reason can be that software bugs 
        and crashes can 
        result in unexpected behavior like flying 
        in random directions.
        & For the fly time, we will make sure 
        we land the drone before it reaches 
        the flight time constraints.
        We will create a handlers script 
        for the software crashes 
        to ensure that Raspberry Pi gets the 
        control again.  \\
        
        Flying drone outdoor without permission 
        & Qatar has very restricted rules regarding flying 
        a drone 
        with a camera outdoor.
        & Get the required permission to fly the drone in 
        Al-Khor airport or fly it indoors inside the 
        university with permission from the department. \\

        Inconsistent performance of the drone in the real
        world compared to the simulation
        & The effectiveness of the trained model based on 
        simulation is yet to be investigated in the real 
        world. It is expected that there will be discrepancies
        between the virtual environment and reality.
        & Design the mobility pattern of the targets in 
        the virtual environment as realistic as possible.
        Moreover, we will perform transfer learning by
        taking the model pre-trained in the simulation
        and training it in the real world. 
        This way, the model weights will be made more 
        suitable for the real world while still benefiting 
        from the convenience of simulation.
        \\

        Incompatibility between the development and 
        runtime environments
        & The development tools, including the \textsc{os}
        and libraries, used for Sphinx, Olympe
        and \gym may not be the same as the runtime ones. 
        For example, developing plugins for Sphinx has to 
        be done on Ubuntu 16.04 only, but running it can be
        done on Ubuntu 18.04.
        & Use Docker to run a suitable container 
        for the development platforms and focus the machine's
        environment only for runtime processes.
        \\

        Accidental premature termination of the 
        training
        & The \gls{rl} training can last for a few
        days. Many things can happen during that
        period such as forgetting to plug in the
        charger, disconnection between 
        Olympe and Sphinx, and sudden shutdown of
        the laptop due to overheating.
        & Save checkpoints of the weights and
        the last learning rate from time to time
        so that the training can be resumed from
        the point before the termination.
        \\
        
        \bottomrule		
    \end{xltabular}
\end{center}

\end{document}
