% Hardware milestones
\begin{center}
    \setcounter{milestonecounter}{0}
    \def\mysection{hardware} % <- change this variable
    \begin{xltabular}{\textwidth}{ X p{5cm} p{9cm} }
        \caption{Senior 2 project milestones for \mysection.}
        \label{tab:milestones-hardware} \\ % <- change this label
        \toprule

        \textit{No.} & \textit{Milestone} 
            & \textit{Description}
        \\

        \midrule
        \endfirsthead

        \caption[]{Senior 2 project milestones for \mysection\ (continued)} \\
        \toprule

        \textit{No.} & \textit{Milestone} 
            & \textit{Description}
        \\

        \midrule
        \endhead

        \showmilestonecounter 
        & Hardware testing and proving
        design constraints parameters
            & Test the design constraints and push the drone and
            hardware components to the limit
        \\
        \showmilestonecounter
        & 3D print design
            & Find best suitable 3D printed design to
            hold the on-board computer.
        \\
        \showmilestonecounter
        & Moving target solution
            & Find best solution for moving targets
            experiments with specific probability
            and mobility pattern.
        \\

        \bottomrule
    \end{xltabular}
\end{center}

% RL milestones
\begin{center}
    \setcounter{milestonecounter}{0}
    \def\mysection{\textsc{rl}} % <- change this variable
    \begin{xltabular}{\textwidth}{ X p{5cm} p{9cm} }
        \caption{Senior 2 project milestones for \mysection.}
        \label{tab:milestones-rl} \\ % <- change this label
        \toprule

        \textit{No.} & \textit{Milestone} 
            & \textit{Description}
        \\

        \midrule
        \endfirsthead

        \caption[]{Senior 2 project milestones for \mysection\ (continued)} \\
        \toprule

        \textit{No.} & \textit{Milestone} 
            & \textit{Description}
        \\

        \midrule
        \endhead

        \showmilestonecounter 
        & Target simulation
            & Simulate the mobility pattern of the targets and their
            appearance
        \\
        \showmilestonecounter
        & New object detection model  % new
            & Replace the object detection model built in Senior 1 with
            another that can uniquely identify the QR codes
        \\
        \showmilestonecounter
        & RL agent training for fixed targets mission
            & Train an agent to complete a mission in which targets'
            locations change every episode based on a distribution but 
            they don't move in the episode.
        \\
        \showmilestonecounter
        & RL performance verification for fixed targets mission
            & Compare the performance of RL with zig-zag and random
            patterns in terms of time and energy
        \\
        \showmilestonecounter
        & RL agent training for mobile targets mission
            & Train an agent to complete a mission in which 3 targets
            moves and 7 targets are fixed throughout an episode.
            Both the movements and locations rely on distributions.
        \\
        \showmilestonecounter
        & Log and video saving feature % new
        & Include logging of the drone's action, \gls{gps} location
        and time for the mission deployment. 
        In addition, save the video from the drone's camera of the
        mission.
        \\
        \showmilestonecounter
        & Prepare the environment for full integration testing % new
        & Modify the environment and agent so that the agent can use
        the learned model in a smaller environment suited for the full
        integration testing.
        \\
        \showmilestonecounter
        & Finalize the report write-up for the simulation and \gls{rl} % new
        & Fulfil the criteria of the design, implementation, testing
        and future sections with regards to the simulation and
        \gls{rl}.
        \\

        \bottomrule
    \end{xltabular}
\end{center}

% UI milestones 


