\begin{center}
    \setcounter{milestonecounter}{0}
    \begin{xltabular}{\textwidth}{ X p{5cm} p{9cm} }
        \caption{Senior 1 project milestones.}
        \label{tab:milestones} \\
        \toprule

        \textit{No.} & \textit{Milestone} 
            & \textit{Description}
        \\

        \midrule
        \endfirsthead

        \caption[]{Senior 1 project milestones (continued)} \\
        \toprule

        \textit{No.} & \textit{Milestone} 
            & \textit{Description}
        \\

        \midrule
        \endhead

        \showmilestonecounter 
        & Simulation environment
            & Setup the environment and be familiar with 
            the software and libraries that will be used.
        \\
        \showmilestonecounter
        & Object detection model
            & Create dataset and start training the model 
            then try to enhance it.
        \\
        \showmilestonecounter 
        & Research hardware interfacing and possible 
        solutions
            & Collect information about possible hardware 
            components and architectures to be used.
        \\
        \showmilestonecounter 
        & Literature review and related work
            & Start reading related work and previous papers 
            related to our topic, compare, criticize, and 
            summarize them.
        \\
        \showmilestonecounter 
        & Hardware architecture and implementation
            & Start grouping the components together 
            and see what is missing and from where to get it.
        \\
        \showmilestonecounter 
        & Enhance the simulation environment
            & Apply the detection model and tweak 
            the environment and improve it.
        \\
        \showmilestonecounter 
        & Hardware testing and proving design constraints 
        parameters
            & Test the design constraints and push the 
            drone and hardware components to the limit.
        \\
        \showmilestonecounter
        & Interim report
            & Finalize the different sections of the report
            and compile them.
        \\
        \showmilestonecounter 
        & Report review and corrections
            & Review the written report with the supervisor
            and make corrections as necessary.
        \\
        \showmilestonecounter 
        & Presentation
            & Create a presentation based on the report
            as well as the introductory video.
        \\

        \bottomrule
    \end{xltabular}
\end{center}
